\documentclass{harnon-cv}


	% personal details
	\author{Laurie Kemmerer}
	\yourwebsite{http//github.com/lkemmerer}
	\youraddress{laurie.kemmerer@gmail.com \\ (503) 866-4437}
	
	
	\begin{document}
	
		\maketitle
		\addheadertext{Skills}
		\starttimeline
			\timelineitem{Languages}{
          \begin{tabular}{p{4cm} p{4cm} p{4cm} }
              Ruby & Javascript & C\# \\
          \end{tabular}
			}
			\timelinespacer
			\timelineitem{Frameworks}{
          \begin{tabular}{p{4cm} p{4cm} p{4cm} }
              Ruby on Rails & Sinatra & ASP.NET MVC \\
          \end{tabular}
      }
			\timelinespacer
			\timelineitem{Databases}{
          \begin{tabular}{p{4cm} p{4cm} p{4cm} }
              PostgreSQL & Mongo & MS SQL Server \\
          \end{tabular}
      }
			\timelinespacer
		\stoptimeline
		\addheadertext{Experience}
		\starttimeline
			\timelineitem{May 2014 \\to Jan 2015}{
				\addsubheader{Software Engineer | CrowdCompass - Portland, OR}
          \vspace{1.5mm}
          \begin{minipage}{1.0\textwidth}\hspace{5mm}
        In my first two months, I collaborated as part of a cross-functional agile team to implement a one-to-one messaging feature.  In implementing the Rails engine that backed this, I worked with devops to foster a more service-oriented architecture and functioned as the liaison between my team and the 3rd party product that we leveraged.  After this, I worked to maintain and add new features to our monolithic Rails apps with an eye towards breaking out functionality into separate services and increasing test coverage.  I also instituted daily standup for the server-side dev team to help bring about an environment more conducive to knowledge sharing and mentorship.
        \end{minipage}
			}
			\timelinespacer
			\timelineitem{May 2013 \\to May 2014}{
				\addsubheader{Senior Software Engineer | Renewable Funding, LLC - Portland, OR}
          \vspace{1.5mm}
          \begin{minipage}{1.0\textwidth}\hspace{5mm}
        While maintaining the projects mentioned previously, I designed and implemented well-factored, service-oriented (Ruby-beyond-Rails) architecture for green-energy-financing applications and loan processing software.
        \end{minipage}
			}
			\timelinespacer
			\timelineitem{Mar 2010 \\to May 2013}{
				\addsubheader{Software Developer | Renewable Funding, LLC - Portland, OR}
          \vspace{1.5mm}
          \begin{minipage}{1.0\textwidth}\hspace{5mm}
        I developed features for a multi-tenant Rails application that connected homeowners with contractors and financing to make energy-efficiency improvements on their property.  In conjunction, I contributed to the GIS (postgis) functionality that enabled energy and cost savings calculations that were tailored to visitors' properties.  I also standardized energy retrofit data from CA local governments and utilities and worked to create a data warehouse of the data.
        \end{minipage}
			}
			\timelinespacer
			\timelineitem{Dec 2008\\to Mar 2010}{
				\addsubheader{Software Engineer | Harland Financial Solutions - Portland, OR}
          \vspace{1.5mm}
          \begin{minipage}{1.0\textwidth}\hspace{5mm}
	      I performed requirements gathering and end-to-end design, development, and maintenance of ASP.NET MVC, Web Form, and Winform applications, which increased user efficiency and revenue recognition and reduced operational cost.  I also advocated for better development processes such as code reviews and thorough documentation of our SDLC.
        \end{minipage}
			}
			\timelinespacer

			\timelineitem{Apr 2007\\ to Dec 2008}{
				\addsubheader{QA Engineer | Harland Financial Solutions - Portland, OR}
          \vspace{1.5mm}
          \begin{minipage}{1.0\textwidth}\hspace{5mm}
	      I clarified requirements for and tested internal web applications by working closely with programmers and clients.  I aided in the debugging process by pinpointing errors and fixing bugs. Eventually, I began performing maintenance on existing applications while learning the value of TDD.
        \end{minipage}
			}
			\timelinespacer

			\timelineitem{Apr 2006\\ to Jan 2007}{
				\addsubheader{Lead QA Technician/Customer Support | Instant Media - Beaverton, OR}
          \vspace{1.5mm}
          \begin{minipage}{1.0\textwidth}\hspace{5mm}
        Responsible for giving final sign-off on builds and database changes, I maintained test documentation and performed ad-hoc, scenario, and usability testing of our internet TV/RSS feed Windows application and company website.  I also managed Tier 1 technical support representatives while integrating support feedback and usability suggestions into design requirements.
        \end{minipage}
			}
			\timelinespacer

			\timelineitem{Sep 2003\\ to Jan 2006}{
				\addsubheader{Lead Technology Tutor | Penn State (Info. Technology Services)}
          \vspace{1.5mm}
          \begin{minipage}{1.0\textwidth}\hspace{5mm}
	      I tutored faculty and administered an efficient one-on-one CMS (course management system) tutoring program that helped 300 faculty clients and increased the efficiency of record keeping and tutor assignment 10-fold.
        \end{minipage}
			}
			\timelinespacer

			\timelineitem{Summer 2005}{
				\addsubheader{Undergraduate Research Assistant | Penn State (HCI Lab)}
          \vspace{1.5mm}
          \begin{minipage}{1.0\textwidth}\hspace{5mm}
	      I aided in the organization and execution of the first technology conference to foster communication among area non-profits about their technology usage, which was attended by over 50 organizations.
          \end{minipage}
			}
		\stoptimeline
		
    \addheadertext{Community Involvement}
		\starttimeline
			\timelineitem{July 2014,\\Nov 2012}{
        \addsubheader{CascadiaJS volunteer/staff}
      }
			\timelinespacer

			\timelineitem{Sep 2012}{
        \addsubheader{RailsGirls PDX coach}
      }
    \stoptimeline
			
		\addheadertext{Education}
		\starttimeline
			\timelineitem{2006}{
				\addsubheader{B.S. Computer Engineering | Penn State - College Park, PA}
        \addtimelinebullet{Schreyer Honors College, 2001-Spring 2004}
        \addtimelinebullet{Society of Women Engineers, Swing Dancing club, Mars Society}
    }
    \stoptimeline
			
	\end{document}
