%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{grey}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Laurie}{Kemmerer}
%\title{Resumé title}                               % optional, remove / comment the line if not wanted
%\address{street and number}{postcode city}{country}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+1~(503)~866~4437}                   % optional, remove / comment the line if not wanted
\email{laurie.kemmerer@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{http://github.com/lkemmerer}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Languages}
\cvitemwithcomment{Java}{Intermediate}{...Like C\#, but it makes me miss Scala}
\cvitemwithcomment{JavaScript}{Advanced}{...better now that there are type-checking libraries}
\cvitemwithcomment{C\#}{Intermediate}{...Like Java, but with better functional features}
\cvitemwithcomment{Scala}{Beginner/Intermediate}{...my current favorite language}
\cvitemwithcomment{Ruby}{Advanced}{...my second favorite language}

\section{Other Technologies, with varying levels of aptitude}
\cvdoubleitem{Databases}{PostgreSQL, MongoDB, MS SQL Server}{Web}{Spark, Ruby on Rails, Sinatra, Akka HTTP, AngularJS, ServiceStack, React/Redux, Express}
\cvdoubleitem{CI}{TravisCI, TeamCity, Jenkins}{Devopsish}{Terraform, Docker, Vagrant}
\cvitem{etc}{Akka, RabbitMQ, AWS}

\section{Experience}
\cventry{Sept 2017 to present}{Software Engineer}{Flightglobal}{Portland, OR}{}{I built the groundwork for a flexible and high performance flight and traveler matching engine. I added features to our traveler services suite of products using microservices built with Java, JavaScript, and Python. We also worked on rewriting the remainder of a 15-year-old Java monolith and refactoring our Angular and Backbone front-ends to use React and Redux.}
\cventry{Sept 2016 to August 2017}{Software Engineer/Team Lead}{ShiftWise}{Portland, OR}{}{As part of the platform team, I helped create the infrastructure for an event-driven application that process high volumes of data and feeds into our reporting team's data lake. It relies on AWS SQS/SNS and Akka's actor system. In February I was made team lead. In addition to existing duties, I facilitate communication with management, other teams, and stakeholders and advocate for my team and their needs.\newline{}\newline{}I also supporting another team as they converted our Windows-based .NET microservices to run on Linux in AWS.}
\cventry{Jan 2016 to Sept 2016}{Software Development Engineer in Test}{ShiftWise}{Portland, OR}{}{I built and maintained testing infrastructure for a next generation vendor management system. I provided guidance about good testing practices and ways to design more maintainable systems through hands-on collaboration and code/test reviews of our C\# and AngularJS application. I and my fellow SDETs promoted communication between teams and propagated evolving design patterns and testing strategies.}
\cventry{Aug 2015 to Jan 2016}{Remote Software Engineer/Contractor}{Zivity}{San Francisco, CA}{}{Using Rails and Backbone, I implemented features for a crowdfunding service that integrates with their existing site.}
\cventry{Feb to May 2015}{Technical Consultant}{Renew Financial}{Portland, OR}{}{I initially worked with the product team to add new features using AngularJS and Ruby. Due to looming deadlines, the QA team asked that I move to their team full time.\newline {
I pair-programmed with QA, mentoring in Ruby and OOP skills. I improved their home-spun framework, making tests more maintainable and less error-prone.}
}
\cventry{May 2014 to Jan 2015}{Software Engineer}{CrowdCompass}{Portland, OR}{}{As part of a cross-functional agile team, I collaborated to deliver a one-to-one messaging feature. I worked with devops to foster a more service-oriented architecture. I functioned as the liaison between my team and the 3rd party whose service we leveraged.
\newline{}\newline {
I maintained and added features to our monolithic Rails apps. In doing so, I increased test coverage and refactored in order to simplify future work to separate functionality into independent services. I also instituted daily standup for the server team and pushed for mandatory code reviews. This helped bring about an environment more conducive to knowledge sharing and mentorship.}
}
\cventry{May 2013 to May 2014}{Senior Software Engineer}{Renewable Funding (now Renew Financial)}{Portland, OR}{}{I designed and implemented well-factored, service-oriented architecture and features for green-energy-financing applications and loan processing software. I maintained existing projects and contributed to a page-object-model framework for use with Cucumber.
}
\cventry{Mar 2010 to May 2013}{Software Developer}{Renewable Funding (now Renew Financial)}{Portland, OR}{}{
Using BDD and TDD, I developed features for a multi-tenant Rails application. This app provided homeowners with energy efficiency information and connections to contractors and financing. I contributed to GIS (postgis) functionality that enabled property-specific savings calculations.
I standardized energy retrofit data from local governments and utilities and used the results to created a data warehouse for reporting purposes.
}
\cventry{Nov 2007 to Mar 2010}{Software Engineer}{Harland Financial Solutions (acquired by D+H)}{Portland, OR}{}{
 I gathered requirements for internal applications that increased user efficiency and revenue recognition. I designed, developed, and maintained these apps using ASP.NET MVC, Web Forms, and Winforms. I advocated for code reviews and other process improvements.
}
\cventry{Apr to Nov 2007}{QA Engineer}{Harland Financial Solutions (acquired by D+H)}{Portland, OR}{}{
I worked with clients and engineers to clarify requirements for internal web applications. I performed manual testing, then aided in the debugging process by pinpointing errors and fixing bugs. Later, I began performing maintenance on existing applications while learning the value of TDD.
}
\cventry{Apr 2006 to Jan 2007}{Lead QA Techician/defacto Customer Support}{Instant Media}{Portland, OR}{}{
 I was responsible for giving final sign-off on builds and database changes. I maintained test documentation and plans for our internet TV/RSS feed Windows application. I performed ad-hoc, scenario, and usability testing.
 \newline {
I managed outsourced technical support representatives and integrated feedback into design requirements.}
}

\section{Education}
\cventry{2001--2006}{B.S. Computer Engineering}{Penn State University}{University Park, PA}{\textit{Grade}}{In addition to gaining a degree, I worked as Lead Technology Tutor for a program that tutored faculty in how to use computers and managed tutor scheduling and assignment.  I also spent a summer working as a research assistant in the Human Computer Interaction lab. During that time, I participated in organizing a conference to help foster communication between non-profits about how they use technology.  }  % arguments 3 to 6 can be left empty

\clearpage
%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.

